%\documentclass[a4paper,10pt]{report}
\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}

% Usepackages, could be moved to a new file
% Long Table and decimal aligned columns
\usepackage{dcolumn}
\usepackage{longtable}

% Mathematics support
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}


% Text Control
\usepackage{xspace}
\usepackage{textcase}
\usepackage{url}%hyperref}

% Graphics
\usepackage{wasysym}
\usepackage{graphics}
\usepackage{graphicx}   % A package to allow insertion of
                        % external image files
\usepackage{epstopdf}
% Comments
\usepackage{comment}
% Citation
%\usepackage{natbib}


\newif\ifrev
% comment out the following line after the revision is proved
%\revtrue
\ifrev
  \usepackage{color}
  \usepackage[normalem]{ulem}
  \newcommand{\add}[1]{\textcolor{blue}{\uline{#1}}}
  \newcommand{\del}[1]{\textcolor{red}{\sout{#1}}}
\else
  \newcommand{\add}[1]{#1}
  \newcommand{\del}[1]{}
\fi

% Title Page
% \title{Design and Implementation for a Peer-to-peer-based Mobile VoIP 
% Application}
% \title{ThinkTogether: A Collaborative App based on a Peer-to-Peer 
% Infrastructure}

\title{Exploring Peer-to-Peer Infrastructure for Computer Supported 
Collaborative Work Applications}

\author{\qquad Tianming Wei \qquad Yongjun Xu \qquad Yiyun Zhao \qquad Nishant Khanna \qquad Bing Gao \qquad Yvonne Coady\\
Department of Computer Science\\
University of Victoria, Victoria, BC, Canada\\}


\begin{document}
\maketitle
\pagestyle{plain}

\begin{abstract}
\begin{comment}
With the enhancement in technology every day there are so many applications 
being developed every day. There are a lot of applications that have been 
developed to record presentations and to upload content onto the server for 
later reference. ThinkTogether is much more than that. Not only does it support 
basic functions like giving presentation, and adding comments and marking 
important points, ThinkTogether also provides multilayer function, which achieve 
better performance by separating different users into multiple layers. As fully 
functionable as the app already is, we still want to take it to the next level. 
In this study, we propose a network mechanism using VoIP technology, to 
introduce voice streaming feature into existing application developed by Two 
Tall Totems.
\end{comment}
Computer Supported Collaborative Work (CSCW) has been greatly enhanced by 
technology that provides almost real-time capture, replay, and sharing of 
content. “The cloud” has popularized ease of deployment for apps serviced 
through a centralized approach. In this work we propose a more aggressive 
design, decentralizing the location of shared content within a peer-to-peer 
structure. Ease of deployment is maintained through a novel architecture for a 
multilayer distributed cloud. This paper describes how this approach has shown 
promise in a prototype app, {\em ThinkTogether}, 
and the potential to enable a consistent user experience, even for remote peers 
sharing VoIP.

\end{abstract}

\begin{IEEEkeywords}
  Voice over IP, Peer-to-peer, Quality of service, Traffic balance, Bandwidth 
utilization.
\end{IEEEkeywords}

%\section{Introduction}
\input{sec_intro}

%\section{Related Work}\label{simu}
\input{sec_rel}

%\section{System Model}
\input{sec_mod}

%\section{The heuristic algorithm}\label{alg}
\input{sec_sim}

%\section{Performance Evaluation}\label{simu}
%\input{sec_eval}

%\section{Conclusion and Further Work}\label{conclu}
\input{sec_con}

%\input{appendix}


\bibliographystyle{plain}
\begin{thebibliography}{10}

\begin{comment}
\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\bibitem{sample}
\newblock ``Efficient user-assisted content distribution over 
information-centric
  network,''
\newblock In {\em Proc. IFIP Networking Conference}, pp. 1--12, 2012.
\end{comment}

%ref 00
\bibitem{XG_P2P_INFO04}
X.~Yang, and G.~Veciana,
\newblock ``Service capacity of peer to peer networks,''
\newblock In {\em IEEE Proc. of the Twenty-third Annual Joint Conference on 
Computer and Communications (INFOCOM)}, pp. 2242--2252, 2004.

%ref 16
\bibitem{A_OMNET_ESM01}
A.~Varga, 
\newblock ``The OMNeT++ discrete event simulation system,''
\newblock In {\em Proc. of the European simulation multiconference (ESM)},
9(185), 2001. 

%ref 01
\bibitem{HS_VoIP_ICTC10}
H.~Wook and S.~Kang, 
\newblock ``Design and implementation of SIP-based mobile VoIP 
application for multiple smartphone OS,'' 
\newblock In {\em Proc. Information and Communication 
Technology Convergence (ICTC)}, pp. 565--568, 2010.

%ref 02
\bibitem{HSR_VoIP_TVT07}
H.~Fathi, S.~S.~Chakraborty, and R.~Prasad,
\newblock ``Optimization of Mobile IPv6-Based Handovers to Support VoIP Services 
in Wireless Heterogeneous Networks,'' 
\newblock In {\em IEEE Transactions on Vehicular Technology}, 56(1):260--270, 
2007. doi: 10.1109/TVT.2006.883806.

%ref 03
\bibitem{HYS_VoIP_COM00}
H.~C.~Rao, Y.~Lin, S.~Cho,
\newblock ``iGSM: VoIP service for mobile networks,'' 
\newblock In {\em IEEE Communications Magazine}, 38(4):62--69, 2000.
 doi: 10.1109/35.833558.

%ref 04
\bibitem{MRSR_VoIP_COM08}
M.~Fong, R.~Novak, S.~Mcbeath, and R.~Srinivasan, 
\newblock ``Improved VoIP capacity in mobile WiMAX systems using persistent 
resource allocation,''
\newblock In {\em IEEE Communications Magazine}, 46(10):50--57, 2008. 
doi: 10.1109/MCOM.2008.4644119.

%ref 05
\bibitem{OR_VoIP_PMC03}
O.~Komolafe and R.~Gardner,  
\newblock ``Aggregation of VoIP streams in a 3G mobile network: a teletraffic 
perspective,''
\newblock In {\em Proc. Personal Mobile Communications Conference}, pp. 
545--549, 2003. doi: 10.1049/cp:20030314.

%ref 06
\bibitem{YRAP_VoIP_MSYS07} 
Y.~Agarwal, R.~Chandra, A.~Wolman, P.~Bahl, K.~Chin, and R.~Gupta,
\newblock ``Wireless wakeups revisited: energy management for voip over WiFi 
smartphones,'' 
\newblock In {\em ACM Proc. of the 5th international conference on Mobile 
systems, applications and services (MobiSys)}, pp. 179--191, 2007. 
doi=10.1145/1247660.1247682.

%ref 07
\bibitem{WPY_VoIP_SYS11}
W.~Chen, P.~Lin, and Y.~Lin, 
\newblock ``Real-Time VoIP Quality Measurement for Mobile Devices,'' 
\newblock In {\em IEEE Systems Journal}, 5(4):538--544, 2011. 
doi: 10.1109/JSYST.2011.2165604.

%ref 08
\bibitem{DHMS_WiMAX_WOW08}
D.~Kim, H.~Cai, M.~Na, S.~Choi, 
\newblock ``Performance measurement over Mobile WiMAX/IEEE 802.16e network,''
\newblock In {\em International Symposium on World of Wireless, Mobile and 
Multimedia Networks (WoWMoM)}, 1(8):23--26, June 2008.
doi: 10.1109/WOWMOM.2008.4594817.
 
%ref 09
\bibitem{SMPM_VoIP_ICAESM12}
S.~Sundar, M.~K.~Kumar, P.~Selvinpremkumar, and M.~Chinnadurai, 
\newblock ``Voice over IP via Bluetooth/Wi-Fi Peer to Peer,'' 
\newblock In {\em International Conference on Advances in Engineering, Science 
and Management (ICAESM)}, pp. 828--837, March 2012.

%ref 10
\bibitem{GWA_P2P_VoIP_ICWMC10}
G.~Kbar, W.~Mansoor, A.~Naim, 
\newblock ``Voice over IP Mobile Telephony Using WiFi P2P,''
\newblock In {\em the 6th International Conference on Wireless and Mobile 
Communications (ICWMC)}, pp. 268--273, September 2010. 
doi: 10.1109/ICWMC.2010.97.
 
%ref 11
\bibitem{GCXZ_P2PVoIP_MTA13}
G.~Wang, C.~Zhang, X.~Qiu, and Z.~Zeng, 
\newblock ``An efficient relay node selection scheme to improve the performance 
of P2P-based VoIP applications in Chinese internet,''
\newblock In {\em Multimedia Tools and Applications}, 64(3):599--625, 2013. 
doi: 10.1007/s11042-011-0952-5.

%ref 12
\bibitem{SN_Skype_CIST05}
S.~Guha and N.~Daswani, 
\newblock ``An Experimental Study of the Skype Peer-to-Peer VoIP System,'' 
\newblock In {\em Computing and Information Science Technical 
Reports}, 2005.

%ref 13
\bibitem{TA_Skype_COMPNET08}
T.~Hoßfeld and A.~Binzenhöfer, 
\newblock ``Analysis of Skype VoIP traffic in UMTS: End-to-end QoS and QoE 
measurements,''
\newblock In {\em Computer Networks}, 52(3):650--666, 2008.
doi: 10.1016/j.comnet.2007.10.008.

%ref 14
\bibitem{SH_Skype_INFO06}
S.~A.~Baset, and H.~Schulzrinne, 
\newblock ``An analysis of the skype peer-to-peer internet telephony protocol,''
\newblock In {\em IEEE Proc. of the 25th IEEE International Conference 
on Computer Communications (INFOCOM)}, pp.1--11, April 2006. 
doi: 10.1109/INFOCOM.2006.312.


%ref 15
\bibitem{JSPS_USPatent05}
J.~Fobert, S.~Navaratnam, P.~J.~Dagert, and S.~J.~McKinnon, 
\newblock ``Client-server network for managing Internet protocol 
voice packets''
\newblock U.S. Patent No. 6,853,713, February 2005.


%ref 17
\bibitem{EI_OMNET_ACT10}
E.~Anggadjaja, and I.~McLoughlin, 
\newblock ``Point-to-point OMNeT++ based simulation of reliable transmission 
using realistic segmentation and reassembly with error control,''
\newblock In {\em IEEE second International Conference on Advances in 
Computing, Control and Telecommunication Technologies (ACT)}, pp. 125--128, 
2010.

%ref 18
\bibitem{MM_OMNET_OMN08}
M.~Bohge, and M.~Renwanz, 
\newblock ``A realistic VoIP traffic generation and evaluation tool for 
OMNeT++,'' 
\newblock In {\em Proc. of the 1st International Workshop on OMNeT++}, 
March 2008.

%ref 19
\bibitem{XX_OMNET_ICQ12}
X.~Qing, and X.~Ren,
\newblock ``Research of routing protocols simulation for wireless sensor 
networks based on OMNeT++,''
\newblock In {\em IEEE International Conference on Quality, Reliability, Risk, 
Maintenance, and Safety Engineering (ICQR2MSE)}, pp. 79--82, June 2012. 

%ref 20
\bibitem{JJ_TEL83}
J.~Postel, and J.~K.~Reynolds, 
\newblock ``Telnet protocol specification,'' 1983.

%ref 21
\bibitem{BJJH_HTTP1999}
R.~Fielding, J.~Gettys, J.~Mogul, H.~Frystyk, L.~Masinter, P.~Leach, and T.~
Berners-Lee, 
\newblock ``Hypertext transfer protocol–HTTP/1.1,'' 1999.

%ref 22
\bibitem{GF_COM00}
G.~Seckin, and F.~Golshani, 
\newblock ``Real-time transmission of multilayer video over ATM networks,''
\newblock In {\em Computer Communications}, 23(10):962--974, 2000.


\end{thebibliography}

%\bibliography{pacrim15}


\end{document}
