\section{Conclusions and Future Work}
In this paper, we have initiated a model which decentralizes the location of
shared content within a P2P structure for a CSCW application (VoIP).
As a part of future work, we aim to extend this application for people who can
download the voice stream from the presentation remotely in real-time. We also
aim to use a hierarchical structure for the network which will help the
different nodes present in the network to change their roles during the
presentation at any time. Once the application is in operation for a limited
number of users, we aim to extend this application in a way so that it
can be used for any number of users without having any storage issues, any
disruption in the voice streaming or any bandwidth issues in the network by
adding large number of users to the presentation. After this we aim to develop 
different use cases for scenarios where the system might have some complications 
and we will try to correct them in a way that is best suited for our application. 
Another thing that we hope to address in the future is that if any of the relayer nodes fails then all
the leaf nodes linked to that relayer will be dynamically transferred to
another relayer. New schemes will be developed to guarantee that these dynamic
changes will not significantly reduce the network performance, as well as to
keep a balanced traffic flow with the optimal bandwidth utilization. Once we have developed 
new schemes for our application, using OMNeT++ we will generate detailed log files 
to analyze the delay in routers during transmission and other parameters that might 
some kind of latency in the application. With the help of these log files we will be able 
to analyze any problems that the application might have in the real-life situation and 
we will try to alter our schemes accordingly to avoid any such problems from occurring in the future. 